The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-07-02 document/ms.tex
words about occurrence rates

\subsection{Catalog of transit candidates}

@@

\section{Empirical search completeness}

@@

\begin{figure*}[p]~\\
\begin{center}
\includegraphics[width=\textwidth]{figures/completeness.pdf}
\end{center}
\caption{%
An empirical estimate of the search completeness as a function of planet
radius and orbital period.
In each bin, the completeness (in percent) is given with the associated
sampling uncertainty.
The projected histograms show the integrated completeness as independent
functions of period and radius.
\dfmfiglabel{completeness}}
\end{figure*}

@@

Using the catalog of exoplanet discoveries (\dfmtodo{some section}) and the
measurement of the search completeness (\dfmtodo{some section}), we can now
estimate the occurrence rate of long-period exoplanets.
This inference can be simplified by making a few strong assumptions that are
only weakly justified.
First, we make the strong assumption that none of the candidates are
astrophysical false positives (background eclipsing binaries, the secondary
eclipse of a long-period binary system, \etc).
We revisit this assumption and discuss its validity in \dfmtodo{some section}.
Next, we model the occurrence of exoplanets as a Poisson process
(\dfmtodo{CITE}) with a rate function $\rate_{\poppars} (R,\,P)$ parameterized
by some parameters \poppars.
This assumption leads to the commonly used likelihood function
(\dfmtodo{CITE})
\begin{eqnarray}
\ln p (\{w_j\}_{j=1}^J\,|\,\poppars) =
    \sum_{j=1}^J \ln \rate_{\poppars} (R_j,\,P_j)
    - \int \rate_{\poppars} (R,\,P)\,Q(R,\,P)\dd R\dd P
    + \mathrm{constant} \quad.
\end{eqnarray}
Since our catalog of discoveries is small, we will only make limited
inferences about the population.
For the purposes of this paper, we will simply estimate the period of
long-period planets ($2\,\mathrm{yr} \le P < 15\,\mathrm{yr}$) in two radius
bins $0.1\,R_\mathrm{J} \le R < 0.5\,R_\mathrm{J}$ and $0.5\,R_\mathrm{J} \le
R < R_\mathrm{J}$.

>>>>

\subsection{Catalog of transit candidates}\sectlabel{catalog}

@@

\section{Empirical search completeness}\sectlabel{completeness}

@@

\begin{figure*}[p]~\\
\begin{center}
\includegraphics[width=\textwidth]{figures/completeness.pdf}
\end{center}
\caption{%
An empirical estimate of the search completeness as a function of planet
radius and orbital period.
In each bin, the completeness is estimated by the fraction of recovered
simulations.
The projected histograms show the integrated completeness as independent
functions of period and radius.
\dfmfiglabel{completeness}}
\end{figure*}

@@

Using the catalog of exoplanet discoveries (\sect{catalog}) and the
measurement of the search completeness (\sect{completeness}), we can now
estimate the occurrence rate of long-period exoplanets.
To simplify the analysis, we will make the strong assumption that none of the
candidates are astrophysical false positives (the eclipse of a stellar mass
companion, a background eclipsing binary, or the secondary eclipse of a
long-period binary system).
We revisit this assumption and discuss its validity in the following section.
As a further simplification, we also neglect the measurement uncertainties on
the planet parameters (including orbital period).
This assumption is only justified because we are only making high-level
measurements of the mean occurrence rate in large bins.
